---
title: "BKT's Basic R Commands Markdowns"
author: "Barbara Talkington<br>King County Regional Homelessness Authority<br> barbara.talkington@kchra.org" #<br> break / enter
#date: '`r format(Sys.time(), "%B %d, %Y")`' #automatic
date: "February 13, 2023" #manually
abstract: "This is an example of an abstract in a paper. This is an example of an abstract in a paper.This is an example of an abstract in a paper. This is an example of an abstract in a paper.This is an example of an abstract in a paper."
fontsize: 12pt
#setup of webpage output
output: bookdown::html_document2 
    #output could also be github_document
    #bookdown is a new library that allows some specifics
# for bibliography
bibliography: Bib_winterschool.bib
  #Bib_winterschool.bib file is not available for our initial import of files so we will need to create it AND save into repo folder on your computer
biblio-style: apalike
csl: apa.csl
# citation styles can be downloaded from online... will there be the same file type... I don't know#
---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r clean history}
# clean memory
rm(list = ls())
```




```{r collecting_DataTable}
# github link to data:
link="https://github.com/eScienceWinterSchool/PythonSession/raw/master/hdidemiso_plus.RDS"

#opening data
fileLink=url(link)
mergedData=readRDS(fileLink)
```

```{r data types}
str(mergedData)
```








## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
```


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{python}

```

